|

### 2019-09-06 inst/manuscript/candidaev_figures.Rmd
Switch CairoPS back to grDevices postscript
Also remove Cairo from Suggests

# arguments for figure 1 export
f1_args <- list(tiff = list(type = "cairo", compression = "lzw"))
```

```{r figure1, fig.width=7.1, fig.height=4, fig.path='figures/', dev=c('pdf', 'CairoPS', 'tiff'), dev.args=f1_args, dpi=600}
# draw figure 1
ggarrange(f1a, 
          ggarrange(f1b, f1c, 
                    labels = c("B", "C"), 
                    ncol = 2,
                    nrow = 1, 
                    widths = c(1.8,1)), 
          labels = c("A", ""), 
          nrow = 2, 
          ncol = 1, 
          heights = c(1,1))
```

@@

# arguments for figure 2 export
f2_args <- list(tiff = list(type = "cairo", compression = "lzw"))
```

```{r figure2, fig.width=7.1, fig.height=6, fig.path='figures/', dev=c('pdf', 'CairoPS', 'tiff'),  dev.args=f2_args, dpi=600}
# draw figure 2
ggarrange(ggarrange(f2a1, f2a2, f2a3, f2a4, 
                    labels = c("A", "", "", ""), 
                    ncol = 4, 
                    nrow = 1, 
                    align = "v"), 
          ggarrange(f2b1, f2b2,
                    f2b3, f2b4, 
                    labels = c("B", rep("", 3)), 
                    ncol = 2, 
                    nrow = 2, 
                    align = "hv", 
                    common.legend = TRUE, 
                    legend = "right", 
                    widths = c(1,1), 
                    vjust = 1), 
          ncol = 1,
          nrow = 2, 
          heights = c(1,2))
```

@@

# arguments for figure 3 export
f3_args <- list(tiff = list(type = "cairo", compression = "lzw"))
```

```{r figure3, fig.width=7.2, fig.height=6, fig.path='figures/', dev=c('pdf', 'CairoPS', 'tiff'),  dev.args=f3_args, dpi=600}
# draw figure 3
ggarrange(f3_y, f3_a9, 
          f3_a1, f3_b, 
          labels = NULL, 
          ncol = 2, 
          nrow = 2, 
          common.legend = TRUE, 
          legend = "bottom", 
          align = "hv")
```

@@

# arguments for figure 4 export
f4_args <- list(tiff = list(type = "cairo", compression = "lzw"))
```

```{r figure4, fig.width=7.1, fig.height=5, fig.path='figures/', dev=c('pdf', 'CairoPS', 'tiff'),  dev.args=f4_args, dpi=600}
ggarrange(ggarrange(f4a, f4b,
                    labels = c("A", "B"),
                    ncol = 2,
                    nrow = 1),
          ggarrange(f4c, f4d,
                    labels = c("C", "D"),
                    ncol = 2,
                    nrow = 1, 
                    common.legend = TRUE,
                    legend = "right", 
                    align = "hv"),
          labels = NULL,
          ncol = 1,
          nrow = 2,
          heights = c(2, 3))
```

@@

# arguments for figure 6 export
f6_args <- list(tiff = list(type = "cairo", compression = "lzw"))
```

```{r figure6, fig.width=2.5, fig.height=4, fig.path='figures/', dev=c('pdf', 'CairoPS', 'tiff'), dev.args=f6_args, dpi=600}
ggarrange(f6a, f6b, 
          labels = c("A", "B"), 
          ncol = 1,
          nrow = 2)

>>>>

# arguments for figure 1 export
f1_args <- list(tiff = list(type = "cairo", compression = "lzw"), 
                postscript = list(bg = "white", fonts = "sans"))
```

```{r figure1, fig.width=7.1, fig.height=4, fig.path='figures/', dev=c('pdf', 'postscript', 'tiff'), dev.args=f1_args, dpi=600}
# draw figure 1
ggarrange(f1a, 
          ggarrange(f1b, f1c, 
                    labels = c("B", "C"), 
                    ncol = 2,
                    nrow = 1, 
                    widths = c(1.8,1)), 
          labels = c("A", ""), 
          nrow = 2, 
          ncol = 1, 
          heights = c(1,1))
```

@@

# arguments for figure 2 export
f2_args <- list(tiff = list(type = "cairo", compression = "lzw"), 
                postscript = list(bg = "white", fonts = "sans"))
```

```{r figure2, fig.width=7.1, fig.height=6, fig.path='figures/', dev=c('pdf', 'postscript', 'tiff'),  dev.args=f2_args, dpi=600}
# draw figure 2
ggarrange(ggarrange(f2a1, f2a2, f2a3, f2a4, 
                    labels = c("A", "", "", ""), 
                    ncol = 4, 
                    nrow = 1, 
                    align = "v"), 
          ggarrange(f2b1, f2b2,
                    f2b3, f2b4, 
                    labels = c("B", rep("", 3)), 
                    ncol = 2, 
                    nrow = 2, 
                    align = "hv", 
                    common.legend = TRUE, 
                    legend = "right", 
                    widths = c(1,1), 
                    vjust = 1), 
          ncol = 1,
          nrow = 2, 
          heights = c(1,2))
```

@@

# arguments for figure 3 export
f3_args <- list(tiff = list(type = "cairo", compression = "lzw"), 
                postscript = list(bg = "white", fonts = "sans"))
```

```{r figure3, fig.width=7.2, fig.height=6, fig.path='figures/', dev=c('pdf', 'postscript', 'tiff'),  dev.args=f3_args, dpi=600}
# draw figure 3
ggarrange(f3_y, f3_a9, 
          f3_a1, f3_b, 
          labels = NULL, 
          ncol = 2, 
          nrow = 2, 
          common.legend = TRUE, 
          legend = "bottom", 
          align = "hv")
```

@@

# arguments for figure 4 export
f4_args <- list(tiff = list(type = "cairo", compression = "lzw"), 
                postscript = list(bg = "white", fonts = "sans"))
```

```{r figure4, fig.width=7.1, fig.height=5, fig.path='figures/', dev=c('pdf', 'postscript', 'tiff'),  dev.args=f4_args, dpi=600}
ggarrange(ggarrange(f4a, f4b,
                    labels = c("A", "B"),
                    ncol = 2,
                    nrow = 1),
          ggarrange(f4c, f4d,
                    labels = c("C", "D"),
                    ncol = 2,
                    nrow = 1, 
                    common.legend = TRUE,
                    legend = "right", 
                    align = "hv"),
          labels = NULL,
          ncol = 1,
          nrow = 2,
          heights = c(2, 3))
```

@@

# arguments for figure 6 export
f6_args <- list(tiff = list(type = "cairo", compression = "lzw"), 
                postscript = list(bg = "white", fonts = "sans"))
```

```{r figure6, fig.width=2.5, fig.height=4, fig.path='figures/', dev=c('pdf', 'postscript', 'tiff'), dev.args=f6_args, dpi=600}
ggarrange(f6a, f6b, 
          labels = c("A", "B"), 
          ncol = 1,
          nrow = 2)

### 2019-09-06 inst/manuscript/candidaev_supplement.Rmd
Switch CairoPS back to grDevices postscript
Also remove Cairo from Suggests

# arguments for figure S2 export
fS2_args <- list(tiff = list(type = "cairo", compression = "lzw"))
```

```{r figureS2, fig.cap=fS2_cap, fig.height=5, fig.width=5, fig.path='figures/', dev=c('pdf', 'CairoPS', 'tiff'), dev.args=fS2_args, dpi=600}
fS2_cap <- c("\\textbf{Size distribution of \\textit{C. albicans} EVs as 
              determined by nanoparticle tracking analysis (NTA).} A line plot 
              for each EV biological replicate from each strain is shown. Each 
              line plots represents the average of three technical replicates 
              and the dashed grey lines indicate 100 nm.")

>>>>

# arguments for figure S2 export
fS2_args <- list(tiff = list(type = "cairo", compression = "lzw"), 
                postscript = list(bg = "white", fonts = "sans"))
```

```{r figureS2, fig.cap=fS2_cap, fig.height=5, fig.width=5, fig.path='figures/', dev=c('pdf', 'postscript', 'tiff'), dev.args=fS2_args, dpi=600}
fS2_cap <- c("\\textbf{Size distribution of \\textit{C. albicans} EVs as 
              determined by nanoparticle tracking analysis (NTA).} A line plot 
              for each EV biological replicate from each strain is shown. Each 
              line plots represents the average of three technical replicates 
              and the dashed grey lines indicate 100 nm.")
